Time-dependent optimized coupled-cluster method for multielectron dynamics

### 2019-04-17 doc/TimeDependence/Draft/Article.tex
added new draft

>>>>

\author{\O yvind Sigmundson Sch\o yen}
\email[Electronic mail:]{o.s.schoyen@fys.uio.no}
\affiliation{Department of Physics, University of Oslo, N-0316 Oslo, Norway}

\author{Sebastian G.~Winther-Larsen}
\email[Electronic mail:]{sebastwi@fys.uio.no}
\affiliation{Department of Physics, University of Oslo, N-0316 Oslo, Norway}

\author{Morten Hjorth-Jensen}
\email[Electronic mail:]{hjensen@msu.edu}
\affiliation{National Superconducting Cyclotron Laboratory and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
